---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
editor_options:
  chunk_output_type: inline
---

```{r Libraries}
library(twitteR)
library(tidyverse)
```
Load necessary libraries.


```{r Data Import and Cleaning}
# Obtain access to the Twitter API using appropriate authentication
api <- '7DPTSeLp9wqmBaoayNYpPJvLp'
apiSecret <- 'ftzB0U2ulWaYs32tNHn9lERkhbVUtbuAiP6o8Lec5XV7lNU7GM'
access <- '1012248144-7qLC5cfX6BVKS1a4lpnIHRndLSPOxiUA62RnEOw'
accessSecret <- 'Qbh5TneWdrQhEkmlDvzOGFKmHzkZVm1KcDzb0kOK13eBP'
setup_twitter_oauth(api, apiSecret, access, accessSecret) 

# Query Twitter API using a function from the twitteR library to obtain a table 
#with the 1000 most recent tweets with the hashtag 'rstats' and relevant 
#information about the tweets
tweets <- searchTwitter("#rstats", 1000)
# Remove retweets
tweets_clean <- strip_retweets(tweets)
# Build a tibble with the name of the tweeter, the content of the tweet, and 
#the number of both favorites and retweets
tweets_tbl <- twListToDF(tweets_clean) %>%
    select(screenName, text, favoriteCount, retweetCount)
```


```{r Analysis}
rt.cor <- cor.test(nchar(tweets_tbl$text), tweets_tbl$retweetCount)
rt.cor
fav.cor <- cor.test(nchar(tweets_tbl$text), tweets_tbl$favoriteCount)
fav.cor
```
Examine the relationship between length of tweet and both number of retweets and number of favorites. The correlation for length of tweet with number of retweets is `r rt.cor$estimate`, and the correlation for length of tweet with number of favorites is `r fav.cor$estimate`.


```{r Visualization}
ggplot(tweets_tbl, aes(x = nchar(text), y = retweetCount)) +
           geom_point() +
    ggtitle("Relationship Between Tweet Length and Retweets") +
    xlab("Length of Tweet") + 
    ylab("Number of Retweets")
ggplot(tweets_tbl, aes(x = nchar(text), y = favoriteCount)) +
           geom_point() + 
    ggtitle("Relationship Between Tweet Length and Favorites") +
    xlab("Length of Tweet") + 
    ylab("Number of Favorites")
```
These plots show the relationship between length of tweet and both number of retweets and number of favorites in the form of a scatterplot. 
